Staged typed type-preserving tagless ``interpreters'', \emph{finally}

### 2007-04-01 tagless/tagless-final.tex
3 edits that escaped the previous check in

When doing PE on fix, we made a deliberate decision to `go all the
way' -- so long as the computation can proceed at the PE stage
(`static value'), we do that rather than residualizing. In the
accompanying source code, we have also implemented an alternative
where fix is unrolled only once and them we residualize. We prefer the
first approach, even though it (unlike the latter) may cause
non-termination at the PE stage -- but \emph{only} if the computation
we are partially evaluating is non-terminating and enough static
information is available to trigger this non-termination.  Our
treatment of fix may lead to the code bloat in the residual
program. That is an issue investigated elsewhere (cite our PEPM2006
paper).

>>>>

When doing partial evaluation on |fix|, we made a deliberate decision to `go all
the way' -- so long as the computation can proceed at the PE stage,
we do that rather than residualizing. In the
accompanying source code, we have also implemented an alternative
where |fix| is unrolled only once and then we residualize. We prefer the
first approach, even though it may cause
non-termination at the PE stage -- but \emph{only} if the computation
we are partially evaluating is non-terminating, and enough static
information is available to trigger this non-termination.  Our
treatment of |fix| may lead to code bloat in the residual
program. That is an issue investigated elsewhere (cite our PEPM2006
paper).
